---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{r}
library(tidyverse)
library(magick)
```



```{css}
body {
    font-family: "Times New roman";
    background-color: #f5f5f5;
}

h1, h2, h3 {
    background-color: transparent;
    font-family: "Helvetica"; 
    font-weight: bold;
}
```

## What's going on with my bus?

This report analyses the busyness levels and the average minutes late my buses are. I was able to explore how busyness levels (based on the number of people on the bus) vary across the buses I take in a week and how many minutes late my buses are on a certain day in the week.

```{r}

# Define the CSV file URL
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTQulEdNNYOnQH-JxQ5L9VXtdYhdSCYaGAruXFseapxGaCH9-efR_R5_zJHFsKtTyg_ZPjg2M9uu3sa/pub?output=csv"

# Read the CSV file
logged_data <- read_csv(csv_file) 

# Change the variable to latest_data and rename the columns
latest_data <- logged_data %>%
  rename(day = 2,
         time = 3,
         minutes_late = 4,  
         busyness_level = 5,  
         experience = 6)
```

## Recent Bus Experience!

```{r}

latest_entry <- latest_data %>% tail(1)

if (latest_entry$experience >= 1 & latest_entry$experience <= 3) {
  cat1 <- image_read("https://media1.tenor.com/m/nBR_oOC_J0YAAAAC/cat-angry.gif") %>%
    image_annotate(text = "Recent bus experience was puur!",
                   color = "#FFFFFF",
                   size = 30,
                   font = "Impact",
                   strokecolor = "#000",
                   stroke = 2,
                   gravity = "north") %>%
    image_scale("300x300")
  
  cat1
  
} else if (latest_entry$experience >= 4 & latest_entry$experience <= 6) {
  cat2 <- image_read("https://media1.tenor.com/m/sCsJ0l1gxHUAAAAd/cat-meme.gif") %>%
    image_annotate(text = "Recent bus experience was just okay!",
                   color = "#FFFFFF",
                   size = 35,
                   font = "Impact",
                   strokecolor = "#000",
                   stroke = 2,
                   gravity = "north") %>%
    image_scale("300x300")
  
  cat2
  
} else if (latest_entry$experience >= 7 & latest_entry$experience <= 9) {
  cat3 <- image_read("https://media1.tenor.com/m/fitGu2TwtHoAAAAd/cat-hyppy.gif") %>%
    image_annotate(text = "Recent bus experience was great!",
                   color = "#FFFFFF",
                   size = 25,
                   font = "Impact",
                   strokecolor = "#000",
                   stroke = 2,
                   gravity = "north") %>%
    image_scale("300x300")
  
  cat3
  
} else if (latest_entry$experience == 10) {
  cat4 <- image_read("https://media1.tenor.com/m/9Nr32cJWZ8oAAAAC/catto.gif") %>%
    image_annotate(text = "PURRFECT!",
                   color = "#FFFFFF",
                   size = 20,
                   font = "Impact",
                   strokecolor = "#000",
                   stroke = 2,
                   gravity = "south") %>%
    image_scale("300x300")
  
  cat4
} 

```

## Summary Values

### max_minutes_late

```{r}
max_minutes_late <- max(latest_data$minutes_late) 
max_day <- latest_data$day[which.max(max_minutes_late)]
paste0("The latest a bus has been so far is ", max_minutes_late, " minutes. The day that has the latest bus is a ", max_day,".")
```

### busyness_count

```{r}
busyness_count <- latest_data %>%
  count(busyness_level) 
max_busyness_count <- max(busyness_count$n)  
max_busyness_level <- busyness_count$busyness_level[which.max(max_busyness_count)]
paste0("The highest count of busyness level is ", max_busyness_count," the busyness level with this count is ", max_busyness_level,".")

```

## Bar Charts

```{r}
ggplot(latest_data, aes(x = factor(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")), 
                 y = minutes_late, fill = day)) +
  geom_bar(stat = "summary", fun = "mean") +
  labs(title = "Average Minutes Late by Day", x = "Day", y = "Mean Minutes Late")
```

```{r}
ggplot(latest_data) +
  geom_bar(aes(x = busyness_level, fill = busyness_level)) +
  labs(title = "Count of Busyness Levels", x = "Busyness Level", y = "Count") +
  theme(axis.text.x = element_blank())
```